```{r, child="aaa.Rmd", include=FALSE}
```

`r descr_models("gen_additive_mod", "vgam")`

## Tuning Parameters

```{r vgam-param-info, echo=FALSE}
defaults <- 
  tibble::tibble(parsnip = c("select_features", "adjust_deg_free"),
                 default = c("FALSE", "1.0"))

param <-
  gen_additive_mod() |>
  set_engine("vgam") |>
  set_mode("classification") |>
  make_parameter_list(defaults)
```

This model has `r nrow(param)` tuning parameters:

```{r, vgam-param-list, echo=FALSE, results='asis'}
param$item
```

## Translation from parsnip to the original package

`r uses_extension("gen_additive_mod", "vgam", "classification")`

```{r vgam-gam}
library(ordered)

gen_additive_mod() %>% 
  set_engine("vgam") %>% 
  set_mode("classification") %>% 
  translate()
```

## Model fitting with smoothers

```{r}
#| child: template-uses-smooth-terms.Rmd
```

```{r}
#| include: false
library(VGAM)
```
```{r}
library(VGAM)
data("income", package = "ordinal")
gen_additive_mod() |> 
  set_engine("vgam") |> 
  set_mode("classification") |> 
  fit(income ~ year + s(pct, df = 2), data = income)

spec <- 
  gen_additive_mod() |> 
  set_engine("vgam") |> 
  set_mode("classification")

workflow() |> 
  add_model(spec, formula = income ~ year + s(pct, df = 2)) |> 
  add_formula(income ~ year + pct) |> 
  # FIXME
  fit(data = income) |> 
  extract_fit_engine()
```

## Preprocessing requirements

```{r}
#| child: template-makes-dummies.Rmd
```

## Case weights

```{r}
#| child: template-uses-case-weights.Rmd
```

_However_, the documentation in [VGAM::vglm()] (which applies also to [VGAM::vgam()]) notes that matrix of case weights can be passed so that different classes have different weights. tidymodels assumes vector of a weights; a matrix cannot be passed in. 

Also, the engine documentation notes that: "The values of `weights` must be positive; try setting a very small value such as `1.0e-8` to effectively delete an observation."

## References

- Yee T. 2010. The VGAM Package for Categorical Data Analysis. _Journal of Statistical Software_ 32(10):1--34. \doi{10.18637/jss.v032.i10}.
